Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-10-22 GWLDCII.tex
spelling and grammar edits

In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams. The main focus of that paper is enumerating the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams that map to the same positroid. The results of the first paper are not needed for this paper.

@@

This paper continues this body of work by establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics literature, and the combinatorics of the assoicated positroid cell (as identified in \cite{wilsonloop}). For instance, a Grassman Necklace is one of the many equivalent combinatorial objects uniquely identifying positroid cells. In this paper, we give an algorithm to read off the Grassmann necklace of the associated positroid cell from the Wilson loop diagram. We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}. This apparent contradiction led to the work in \cite{non-orientable}, which showed that the actual geometric space defined by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.

@@

Finally in Section~\ref{sec poles} we characterize the denominator of the integrand of a Wilson loop diagram in terms the associated matrix and the Grassmann necklace. This characterization is given explicitly by Algorithm~\ref{alg WLD to denom via GN} and Theorem~\ref{thm denom}. Given the physically correct representation of the positroid cell assoicated to a Wilson loop diagram, the irreducible factors of the denominator are exactly the set of irreducible factors of the minors of said representation given by the Grassmann necklace.

@@

One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}, where the volume is determined by the external particles involed. Specifically, the integrand is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}x_{p_r}}{R(W)} \;, \end{equation} multiplied by a $\delta$ function that evaluates the matrix $C(W)$ on the external particles. The denominator $R(W)$ is given in Definition~\ref{def R(W)} below. For the purposes of this paper, we restrict our attention to $\Omega(W)$ only, and ignore the $\delta$ function in the integrand of $I(W)$. The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the integrand of $I(W)$.

@@

This formulation for the denominator comes from the physics literature: see equation (2) in \cite{HeslopStewart}. In Section \ref{sec poles}, we give a geometric meaning to the factors, $\{R_e | e \in V\}$, of $R(W)$.  Given a Grassmann necklace representation of the positroid cell $\Sigma(W)$ ((see Definition~\ref{def:grassmann necklace} and Algorithm \ref{alg:put GN on WLD}), the $R_e$ are exactly the irreducible factors of the minors of $C(W)$ defined by the Grassman necklace. In particular, \emph{which} minors of $C(W)$ contribut to $R(W)$ is geometrically determined. 
We end this section with an example of computing $C(W)$ and $R(W)$ for a particular Wilson loop diagram $W$.

>>>>

In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams. The main focus of that paper is enumerating the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams that map to the same positroid. The results of the first paper are not a prerequisite for this paper.

@@

This paper continues this body of work by establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics literature, and the combinatorics of the associated positroid cell as identified in \cite{wilsonloop}. In this paper we give an algorithm to read off a combinatorial characterization (namely the Grassmann necklace, see Definition~\ref{def:grassmann necklace}) of the associated positroid cell from the Wilson loop diagram itself. We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}. This apparent contradiction led to the work in \cite{non-orientable}, which showed that the actual geometric space defined by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$-dimensional manifold in $\Gr(k,n)$.

@@

Finally, in Section~\ref{sec poles} we characterize the denominator of the integrand of a Wilson loop diagram in terms of its associated matrix and Grassmann necklace. We show that given the physically correct representation of the positroid cell associated to a Wilson loop diagram, the irreducible factors of the denominator are exactly the set of irreducible factors of the minors of said representation given by the Grassmann necklace. This characterization is given explicitly by Algorithm~\ref{alg WLD to denom via GN} and Theorem~\ref{thm denom}.

@@

One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}, where the volume is determined by the external particles involved. Specifically, the integrand is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}x_{p_r}}{R(W)} \;, \end{equation} multiplied by a $\delta$ function that evaluates the matrix $C(W)$ on the external particles. The denominator $R(W)$ is given in Definition~\ref{def R(W)} below. For the purposes of this paper, we restrict our attention to $\Omega(W)$ only, and ignore the $\delta$ function in the integrand of $I(W)$. The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the integrand of $I(W)$.

@@

This formulation for the denominator comes from the physics literature: see equation (2) in \cite{HeslopStewart}. In Section \ref{sec poles}, we give a geometric meaning to the factors $\{R_e\ |\ e \in V\}$ of $R(W)$.  Specifically: given a Grassmann necklace representation of the positroid cell $\Sigma(W)$ (see Definition~\ref{def:grassmann necklace} and Algorithm \ref{alg:put GN on WLD}), the $R_e$ are exactly the irreducible factors of the minors of $C(W)$ defined by the Grassmann necklace. In particular, the question of \emph{which} minors of $C(W)$ contribute to $R(W)$ is geometrically determined.

We end this section with an example of computing $C(W)$ and $R(W)$ for a particular Wilson loop diagram $W$.
